### 2017-08-28 Paper01_EnthalpyAndCrystallization.tex
Results - Annealing XRD - noted which phases match which Tx1-5, other minor edits throughout

\begin{table}[h]
	\centering
	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
	\begin{tabular}{ c c c }
		\toprule
		\acrshort{eds} Analysis & Bulk (at\%)  & Film (at\%)  \\
		\midrule
		Mg & $64.85 \pm 3.18$ & $62.92 \pm 3.24$ \\
		Zn & $29.55 \pm 0.82$ & $31.17 \pm 0.95$ \\
		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.91 \pm 0.19$ \\ 
		\bottomrule
	\end{tabular}
	\label{tab:EDS_Composition}
\end{table}

@@

@@

\todo{peak shift can be seen in the annealing xrd. can make a table of that, but rates of nucleation is only seen in the dynamic.}

@@

\begin{table}[b]
	\centering
	\caption{Supplementary: Annealing \acrshort{xrd} peak pattern list. Peaks which appear in both the bulk and film are marked "Both," peaks only appearing on the bulk are marked "Bulk Only," and peaks only appearing on the film are marked "Film Only."}
	\begin{tabular}{cccccccccc}
		\toprule
		\multicolumn{2}{c}{Mg} & \multicolumn{2}{c}{\MgZn} & \multicolumn{2}{c}{\CaMgZnFive} & \multicolumn{2}{c}{\CaMgZnThirteen} & \multicolumn{2}{c}{MgZn} \\
		\midrule
		32.264 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.636 & Both \\
		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.752 & Both \\
		36.7065 & Both & 19.429 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
		47.925 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.58 & Both \\
		63.2 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
		67.4268 & Both & 27.668 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
		68.7541 & Both & 30.4946 & Bulk Only & 30.3272 & Both & 27.947 & Both & 33.797 & Both \\
		70.121 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
		72.6686 & Both & 34.0114 & Both & 34.2311 & Both & 30.699 & Both & 35.892 & Both \\
		77.9616 & Both & 36.3948 & Both & 34.9708 & Bulk Only & 31.589 & Both & 37.121 & Both \\
		81.7143 & Both & 36.9487 & Bulk Only & 36.3289 & Both & 33.929 & Both & 38.101 & Both \\
		&  & 37.8181 & Both & 37.6976 & Both & 35.308 & Both & 39.312 & Both \\
		&  & 39.1701 & Both & 38.1445 & Both & 35.892 & Bulk Only & 40.416 & Both \\
		&  & 42.4369 & Both & 39.7631 & Both & 36.806 & Both & 41.989 & Both \\
		&  & 43.2937 & Both & 41.2057 & Both & 37.281 & Both & 42.824 & Both \\
		&  & 44.8168 & Both & 42.441 & Both & 38.269 & Both & 43.917 & Both \\
		&  & 47.9318 & Both & 43.9276 & Both & 40.041 & Both & 47.046 & Both \\
		&  & 57.4692 & Both & 45.3071 & Both & 40.991 & Both & 48.376 & Both \\
		&  & 63.2267 & Both & 48.1674 & Both & 42.195 & Both & 49.498 & Both \\
		&  & 64.1349 & Film Only & 52.0808 & Both & 43.038 & Both & 51.285 & Both \\
		&  & 65.0419 & Bulk Only & 53.6599 & Both & 43.917 & Both & 53.211 & Both \\
		&  & 65.3533 & Film Only & 56.9387 & Both & 44.6 & Both & 55.66 & Both \\
		&  & 68.5726 & Bulk Only & 58.561 & Both & 45.306 & Both & 57.955 & Both \\
		&  & 70.0382 & Both & 60.5081 & Both & 46.535 & Both & 60.026 & Both \\
		&  & 72.6234 & Both & 61.853 & Both & 47.306 & Film Only & 62.26 & Both \\
		&  & 76.4763 & Bulk Only & 62.9999 & Both & 48.104 & Bulk Only & 63.687 & Both \\
		&  & 77.2025 & Bulk Only & 64.3501 & Both & 50.079 & Both & 65.186 & Both \\
		&  & 78.3347 & Both & 65.632 & Both & 51.285 & Both &  &  \\
		&  & 82.0596 & Both & 66.831 & Both & 56.178 & Bulk Only &  &  \\
		&  &  &  & 68.7827 & Both & 58.601 & Both &  &  \\
		&  &  &  & 70.1095 & Both & 59.94 & Both &  &  \\
		&  &  &  & 71.8163 & Both & 62.028 & Both &  &  \\
		&  &  &  & 72.8322 & Bulk Only & 63.59 & Both &  &  \\
		&  &  &  & 74.9981 & Both & 64.427 & Both &  &  \\
		&  &  &  & 78.083 & Both & 66.229 & Both &  &  \\
		&  &  &  & 81.5094 & Bulk Only & 67.362 & Both &  &  \\
		&  &  &  & 82.6818 & Film Only & 68.198 & Both &  &  \\
		&  &  &  & 83.1204 & Both & 69.524 & Both &  &  \\
		&  &  &  &  &  & 70.48 & Both &  &  \\
		&  &  &  &  &  & 72.032 & Bulk Only &  &  \\
		&  &  &  &  &  & 73.329 & Both &  &  \\
		&  &  &  &  &  & 73.997 & Bulk Only &  &  \\
		&  &  &  &  &  & 76.736 & Both &  &  \\
		&  &  &  &  &  & 78.69 & Both &  &  \\
		&  &  &  &  &  & 79.631 & Both &  & \\
		%\bottomrule
	\end{tabular}
	\label{tab:Sub_Annealing_XRD_Peaks}
\end{table}

>>>>

\begin{table}[h]
	\centering
	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
	\begin{tabular}{ c c c }
		\toprule
		\acrshort{eds} Analysis & Bulk (at\%)  & Film (at\%)  \\
		\midrule
		Mg & $64.85 \pm 3.18$ & $63.20 \pm 3.28$ \\
		Zn & $29.55 \pm 0.82$ & $30.95 \pm 0.96$ \\
		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
		\bottomrule
	\end{tabular}
	\label{tab:EDS_Composition}
\end{table}

@@

Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}. With \MgZn~ and Mg corresponding to either \Tx $_{1}$ or \Tx $_{2}$, \CaMgZnFive~ to \Tx$_{3}$, MgZn to \Tx$_{4}$, and \CaMgZnThirteen~ to \Tx$_{5}$.

@@

@@

\begin{table}[b]
	\centering
	\caption{Supplementary: Annealing \acrshort{xrd} $2 \theta$ peak pattern list. Peaks which appear in both the bulk and film are marked "Both," peaks only appearing on the bulk are marked "Bulk Only," and peaks only appearing on the film are marked "Film Only."}
	\begin{tabular}{cccccccccc}
		\toprule
		\multicolumn{2}{c}{Mg} & \multicolumn{2}{c}{\MgZn} & \multicolumn{2}{c}{\CaMgZnFive} & \multicolumn{2}{c}{\CaMgZnThirteen} & \multicolumn{2}{c}{MgZn} \\
		\midrule
		32.264 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.636 & Both \\
		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.752 & Both \\
		36.7065 & Both & 19.429 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
		47.925 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.58 & Both \\
		63.2 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
		67.4268 & Both & 27.668 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
		68.7541 & Both & 30.4946 & Bulk Only & 30.3272 & Both & 27.947 & Both & 33.797 & Both \\
		70.121 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
		72.6686 & Both & 34.0114 & Both & 34.2311 & Both & 30.699 & Both & 35.892 & Both \\
		77.9616 & Both & 36.3948 & Both & 34.9708 & Bulk Only & 31.589 & Both & 37.121 & Both \\
		81.7143 & Both & 36.9487 & Bulk Only & 36.3289 & Both & 33.929 & Both & 38.101 & Both \\
		&  & 37.8181 & Both & 37.6976 & Both & 35.308 & Both & 39.312 & Both \\
		&  & 39.1701 & Both & 38.1445 & Both & 35.892 & Bulk Only & 40.416 & Both \\
		&  & 42.4369 & Both & 39.7631 & Both & 36.806 & Both & 41.989 & Both \\
		&  & 43.2937 & Both & 41.2057 & Both & 37.281 & Both & 42.824 & Both \\
		&  & 44.8168 & Both & 42.441 & Both & 38.269 & Both & 43.917 & Both \\
		&  & 47.9318 & Both & 43.9276 & Both & 40.041 & Both & 47.046 & Both \\
		&  & 57.4692 & Both & 45.3071 & Both & 40.991 & Both & 48.376 & Both \\
		&  & 63.2267 & Both & 48.1674 & Both & 42.195 & Both & 49.498 & Both \\
		&  & 64.1349 & Film Only & 52.0808 & Both & 43.038 & Both & 51.285 & Both \\
		&  & 65.0419 & Bulk Only & 53.6599 & Both & 43.917 & Both & 53.211 & Both \\
		&  & 65.3533 & Film Only & 56.9387 & Both & 44.6 & Both & 55.66 & Both \\
		&  & 68.5726 & Bulk Only & 58.561 & Both & 45.306 & Both & 57.955 & Both \\
		&  & 70.0382 & Both & 60.5081 & Both & 46.535 & Both & 60.026 & Both \\
		&  & 72.6234 & Both & 61.853 & Both & 47.306 & Film Only & 62.26 & Both \\
		&  & 76.4763 & Bulk Only & 62.9999 & Both & 48.104 & Bulk Only & 63.687 & Both \\
		&  & 77.2025 & Bulk Only & 64.3501 & Both & 50.079 & Both & 65.186 & Both \\
		&  & 78.3347 & Both & 65.632 & Both & 51.285 & Both &  &  \\
		&  & 82.0596 & Both & 66.831 & Both & 56.178 & Bulk Only &  &  \\
		&  &  &  & 68.7827 & Both & 58.601 & Both &  &  \\
		&  &  &  & 70.1095 & Both & 59.94 & Both &  &  \\
		&  &  &  & 71.8163 & Both & 62.028 & Both &  &  \\
		&  &  &  & 72.8322 & Bulk Only & 63.59 & Both &  &  \\
		&  &  &  & 74.9981 & Both & 64.427 & Both &  &  \\
		&  &  &  & 78.083 & Both & 66.229 & Both &  &  \\
		&  &  &  & 81.5094 & Bulk Only & 67.362 & Both &  &  \\
		&  &  &  & 82.6818 & Film Only & 68.198 & Both &  &  \\
		&  &  &  & 83.1204 & Both & 69.524 & Both &  &  \\
		&  &  &  &  &  & 70.48 & Both &  &  \\
		&  &  &  &  &  & 72.032 & Bulk Only &  &  \\
		&  &  &  &  &  & 73.329 & Both &  &  \\
		&  &  &  &  &  & 73.997 & Bulk Only &  &  \\
		&  &  &  &  &  & 76.736 & Both &  &  \\
		&  &  &  &  &  & 78.69 & Both &  &  \\
		&  &  &  &  &  & 79.631 & Both &  & \\
		%\bottomrule
	\end{tabular}
	\label{tab:Sub_Annealing_XRD_Peaks}
\end{table}
